Quasi-likelihood models

### 2021-09-30 text/Rmd/map-projections/index.Rmd
Cleaned up some Rmd files

---
title: "Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

>>>>

---
title: "Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---
install.packages("rnaturalearthhires", repos="http://packages.ropensci.org", type="source")

### 2021-09-30 text/Rmd/quasi-likelihood/index.Rmd
Cleaned up some Rmd files

---
title: "Direct standardization of mortality rates"
author: "Steve Simon"
source: "New"
date: "2020-09-20"
categories:
- Blog post
tags:
- Gneralized linear model
output: html_document
---

>>>>

---
title: "Quasi-likelihood models"
author: "Steve Simon"
source: "New"
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---
